Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Added code for general analyses: number of studies and plot of publications per year

# Filter the FMD data
fmd_data <- compact_data_with_citation_keys %>% 
  filter(disease == 'fmd') 
```

>>>>

# Filter the FMD data
fmd_data <- compact_data_with_citation_keys %>% 
  filter(disease == 'fmd') 
```
# General analyses

## Number of studied included
Number of studies included `r nrow(compact_data_with_citation_keys)` in review.

## Breakdown of studies before and after 2005
```{r}
before_2005 <- data_without_fmd %>% 
  select(publication_year) %>% 
  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
  count(before_2005) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front")

knitr::kable(before_2005)
```

## Publications per year
```{r}
publications_per_year <- data_without_fmd %>%
  count(publication_year)

publications_per_year_plot <- ggplot(data = publications_per_year) +
  geom_bar(aes(x = publication_year,
               y = n
               ),
           stat = 'identity',
           color = 'black',
           fill = 'tomato3'
           ) +
  scale_y_continuous(breaks = seq(0, 30, 2),
                     labels = seq(0, 30, 2)
                     ) +
  labs(x = "Year of publication", y = "Number of papers") +
  theme_minimal(base_size = 12)

plot(publications_per_year_plot)

# Save to github
ggsave(filename = "publications_per_year.tiff",
       plot = publications_per_year_plot,
       device = 'tiff',
       path = figs_dir
       )

# Save to dropbox folder
ggsave(filename = "fig2_publications_per_year.png",
       plot = publications_per_year_plot,
       device = 'tiff',
       path = dropbox_figs_dir
       )
```
